Web Processing - Standardised GIS Analyses for Cable Route Planning

### 2023-02-09 paper/methods.tex
Added Docker/Docker-Compose files. Not working with the jupyter notebooks.
In general fixed spelling.

added to latex:
 - description of starting end ending points,
 - first bits on the aggregation algorithm
 - figs of cost raster -> aggregated costs -> least cost path
 - a first part on the restricted search space by a buffer

>>>>

The whole stack of the cost raster, via the aggregated costs to the resulting least cost path can is shown with an example for a starting cost raster of 50~m resolution and a rasterization with all touched False (see \ref{fig:costs2path}).
Because of the early stopping strategy used in the aggregation sub-paths with high costs have not been fully computed.Instead the execution stops early after reaching the end point. Because the end point ends at a power transformer, which is a building type, the paths ends at in a Prohibited Area. Therefore areas even farther away from the starting point have been explored first.

\begin{figure}
	\centering

	\subfloat[\centering Cost Raster.]{{\includegraphics[width=.25\linewidth]{./images/CostRasterExample.png} }}%
	\qquad
	\subfloat[\centering Aggregated Cost Raster.]{{\includegraphics[width=.25\linewidth]{./images/AggregatedCosts.png} }}%
	\qquad
	\subfloat[\centering Least Cost Path.]{{\includegraphics[width=.25\linewidth]{./images/LeastCostPathExample.png} }}%

	\caption{Figures of Cost raster and the resulting aggregated Costs and the least cost path for a resolution of 50~m.}
	\label{fig:costs2path}
\end{figure}

### 2023-02-09 paper/paper-CableRoute.tex
Added Docker/Docker-Compose files. Not working with the jupyter notebooks.
In general fixed spelling.

added to latex:
 - description of starting end ending points,
 - first bits on the aggregation algorithm
 - figs of cost raster -> aggregated costs -> least cost path
 - a first part on the restricted search space by a buffer

@@

	\todo{discuss aggregation with max vs sum}
	\todo{Scaling with multiple endpoints.}
	\todo{discuss other methods. Off algorithmic speed-ups}
	\todo{discuss other technical methods of speed-ups, as precompilation, JIT, vector units, multi-core}
	\section{Related Works}\label{sec:related-works}

>>>>

	The aggregation is implemented in a priority queue. 
	Hence a point with a lower cost is evaluated earlier as a starting position to evaluate the cost of its neighbors, than a point with higher costs.
	The aggregation is implemented with early stopping. 
	After the last end point has been has got an aggregated cost the aggregation stops and the back tracking starts.

@@

	Difference aggregation of the rule of a cost raster with max vs sum

	Scaling with multiple endpoints.
	Not algorithmic speed-ups as precompilation, JIT, vector units, multi-core
	\section{Related Works}\label{sec:related-works}

### 2023-02-09 paper/results.tex
Added Docker/Docker-Compose files. Not working with the jupyter notebooks.
In general fixed spelling.

added to latex:
 - description of starting end ending points,
 - first bits on the aggregation algorithm
 - figs of cost raster -> aggregated costs -> least cost path
 - a first part on the restricted search space by a buffer

\subsection{Least Cost Paths}\label{subsec:least-cost-paths}
For each resolution the costs paths were estimated for the rasterization with setting all\_touched False
and all\_touched True.
The distance of both paths is calculated with the mean minimum distance.
For every vertex $P_i$ in the path $L_1$ the minimum between the vertex and the path $L_2$
is computed and afterwards the minimum distances are averaged (see equation~\ref{eq:1}).
\begin{equation}
	\label{eq:1}
	d_{mean} = \frac{1}{|L_1|} \sum_{i=1}^{n} d_{min}(p_i, L_2) \bigg\vert p_i \in L_1
\end{equation}

@@

Hence, the mean minimum euclidean distance between the two paths can used to compute
the similarity.
As different table~\ref{tab:2} shows the distance between the two paths decreases
with increasing resolution.
In addition, this tendency is depicted in figure~\ref{fig:paths_resolution} for the calculated cost paths of 5m and 100 m resolutions.

@@

The total execution time consists of two parts. 
The aggregation of the costs and the back tracking of the least cost to find the path.
\todo{Find out whether back tacking scales linear or square.}

@@

The final least costs paths should between the least cost paths of the lower resolution, with a tendency to be nearer to the paths resulted by the all touched false rasterization.
The first step is to optimize the calculation speed is, only to calculated the least cost paths for this smaller area.
Another method, is to improve the prediction of the medium resolution itself and thus reduce the need for a computation in higher resolution.
\subsubsection{Compare least cost paths, for overlay of both rasterizations}
As all touched true rasterization overestimates and all touched true underestimates the real costs.
A weighted mean will describe the real costs more precise.
As present work indicates, that the weight should favor the all touched false raster.
The best weight should be the percentage of the pixel, which is covered by the object, but this can not be computed in this work.
Thus, the best weight has to be searched.
An alternative might be to compute the cost raster in higher resolution, but than to reproject the to a smaller resolution with a using a (linear) interpolation of the of the weights.\todo{test this idea}
\subsubsection{Compare least cost paths, for down sampled cost paths}
As an alternative to the super position of the all touched true and false raster for the same resolution, the all touched false raster was down sampled to 10~m, 25~m, 50~m and 100~m with bi-linear interpolation.
With this method smaller structures still can be seen in the cost raster, although the resolution is reduced.

% \subsubsection{Restrict search to a minimum sized bounding box}
\subsubsection{Restrict search to a convex hull}
\todo{Construct a polygon form the two lines. Buffer the polygon.}
\todo{max minimum path distance}
\todo{crossing points of two paths}
\subsubsection{Restrict search to reachable points}
For this purpose the aggregated cost as to converted back into a raster.

>>>>

\subsection{Least Cost Paths}\label{subsec:least-cost-paths}
For each resolution the costs paths were estimated for the rasterization with setting all\_touched False
and all\_touched True.

The hypothetical path starts at a transformer about 6~km north the container terminal Bremerhaven and then end at a transformer in the south east of the Osterholz county.

The distance of both paths is calculated with the mean minimum distance.
For every vertex $P_i$ in the path $L_1$ the minimum between the vertex and the path $L_2$
is computed and afterwards the minimum distances are averaged (see equation~\ref{eq:1}).
\begin{equation}
	\label{eq:1}
	d_{mean} = \frac{1}{|L_1|} \sum_{i=1}^{n} d_{min}(p_i, L_2) \bigg\vert p_i \in L_1
\end{equation}

@@

Hence, the mean minimum euclidean distance between the two paths can used to compute
the similarity.
As different table~\ref{tab:2} shows the distance between the two paths decreases
with increasing resolution.
In addition, this tendency is depicted in figure~\ref{fig:paths_resolution} for the calculated cost paths of 5~m and 100~m resolutions.

In contrast the largest distance between the paths (see equation~\ref{eq:2}) will be used, to estimate the minimum distance to the areas that still should be examined to grantee a, that at least cost path found in this limited space is still likely to be optimal.

@@

The total execution time consists of two parts. 
The aggregation of the costs and the back tracking of the least cost to find the path.
\todo{back tacking scales with number of points.}

@@

The final least costs paths should between the least cost paths of the lower resolution, with a tendency to be nearer to the paths resulted by the all touched false rasterization.
The first step is to optimize the calculation speed is, only to calculated the least cost paths for this smaller area.
Another method, is to improve the prediction of the medium resolution itself and thus reduce the need for a computation in higher resolution.
\subsubsection{Compare least cost paths, for overlay of both rasterizations}
As all touched true rasterization overestimates and all touched true underestimates the real costs.
A weighted mean will describe the real costs more precise.
As present work indicates, that the weight should favor the all touched false raster.
The best weight should be the percentage of the pixel, which is covered by the object, but this can not be computed in this work.
Thus, the best weight has to be searched.
An alternative might be to compute the cost raster in higher resolution, but than to reproject the to a smaller resolution with a using a (linear) interpolation of the of the weights.

While the aggregated thus can be speed up.
The time needed for the back tracking stays unchanged.

\subsubsection{Compare least cost paths, for down sampled cost paths}
As an alternative to the super position of the all touched true and false raster for the same resolution, the all touched false raster was down sampled to 10~m, 25~m, 50~m and 100~m with bi-linear interpolation.
With this method smaller structures still can be seen in the cost raster, although the resolution is reduced.

% \subsubsection{Restrict search to a minimum sized bounding box}
\subsubsection{Restrict search to a buffered around the least cost paths}
Construct a polygon form the two lines.
Buffer the polygon with twice the max minimum path distance.

This enabled the possibility  to run a 2.5~m resolution cost raster and clip it to the extent of the polygon. 
This clipped 2.5~m raster for all touched true did only slightly change the path. 
While the all touched False raster, leads to a totally new segment at the end of the path. 
Due to the small resolution, that a small path with the extent of about 2.5 m width became passable. This small path is a power line next to road between which build a cone in a protected landscape area.
The street and the protected landscape area are both restricted areas, while the power line is preferential.
This showing, that the way the cost raster is created in the first place can play a vital role, in the end result. So that a nuance, can cause a detour.
When this behavior occurs, the polygon can not grantee to include the least cost path.
Therefore this polygon should be overlayed with a polygon around the shortest path.

\subsubsection{Restrict search to reachable points}
For this purpose the aggregated cost as to converted back into a raster.
